---
title: "Homework 4 -- QTM 150"
author: "Minh-Thy Tyler"
output: html_document
---


```{r, include=FALSE}
library(tidyverse)
```

## Homework 3

**1** (2 pt). Install the package `babynames` in your computer. Then, load the package in the R chunk below.

```{r}
library(babynames)
# Your answers here
```

**2** (2 pt). The `babynames` package sometimes does not show in the environment, but it is there (type `babynames` to check). How many babynames we have in the dataset?

```{r}
babynames
nrow(babynames)
# There are 1,924,665 babynames, nrow factor to check
```

**3** (2 pt). Print the head and the tail of the `babynames` dataset.

```{r}
head(babynames)
tail(babynames)
# Your answers here
```

**4** (2 pt). Make a barplot of the number of babynames each year (hint: it is going to look ugly because there are many years...)

```{r}
barplot(table(babynames$year))
# Your answers here
```

**5** (2 pt). The babyname in the position 1333029 is Charlotte in 2000. Print the all the variables for the Charlotte in this position.

```{r}
babynames[1333029,]
# Your answers here
```